---
title: Classwork 4
subtitle: The Layered Grammar of Graphics
date: 2025-02-03
from: markdown+emoji
---

```{r}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)
library(DT)
library(gridExtra)
library(gapminder)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 90,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```


```{r}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)
library(DT)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 90,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```

# Question 1. Geometric Objects

## Q1a.
Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.

```{r}
#| echo: true
#| eval: false

ggplot(data = mpg, 
       mapping = aes(x = displ, y = hwy, 
                     color = drv)) +
  geom_point(alpha = .4) +
  geom_smooth(se = FALSE)

```


<br>

## Q1b.
What does `show.legend = FALSE` do? What happens if you remove it? 

```{r}
#| echo: true
#| eval: false

ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, 
                           color = drv),
             alpha = .5,
             show.legend = FALSE)
```


**Answer:** 


<br>

## Q1c.
Recreate the R code necessary to generate the following graphs.

### (a)
```{r}
#| echo: false
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(alpha = .4) +
  geom_smooth(se = FALSE)
```

<br>

### (b)
```{r}
#| echo: false
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(group = drv), 
              se = FALSE) +
  geom_point(alpha = .4)

```

<br>


### (c)
```{r}
#| echo: false
ggplot(mpg, aes(x = displ, y = hwy, 
                color = drv)) +
  geom_point(alpha = .4) +
  geom_smooth(se = FALSE)

```

<br>


### (d)
```{r}
#| echo: false
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(color = drv), alpha = .4) +
  geom_smooth(se = FALSE)

```

<br>

### (e)
```{r}
#| echo: false
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(color = drv), alpha = .4) +
  geom_smooth(aes(linetype = drv), se = FALSE)

```

<br>

### (f)
```{r}
#| echo: false
ggplot(mpg, 
       aes(x = displ, y = hwy)) +
  geom_point(size = 4, color = "white") +
  geom_point(aes(color = drv), alpha = .4) +
  theme_gray()
```

<br>


## Q1d.
- Use the data.frame, `organdata_simple` to visualize the yearly trend of the variable `donors` for each country.
```{r}
organdata_simple <- read_csv('https://bcdanl.github.io/data/organdata_simple.csv')
```

<br><br><br>

# Question 2. Statistical Transformation and Position Adjustment

## Q2a.
What does `geom_col()` do? How is it different to `geom_bar()`?

**Answer**:



<br><br>

## Q2b.
- Install the R package, `nycflights13`, which provides the `flights` data.frame.

```{r}
#| eval: false
flights <- nycflights13::flights
airlines <- nycflights13::airlines

flights <- flights |> 
  left_join(airlines)
```

- Visualize the distribution of `carrier`.

- Visualize how the distribution of `carrier` varies by `origin`.

**Answer**:



<br><br>



# Question 3. Work a little more with gapminder data

```{r}
library(gapminder)
p <- ggplot(data = gapminder,
            mapping = aes(x = gdpPercap,
                          y = lifeExp))
p + 
  geom_point() +
  geom_smooth()
```

## Q3a.
- What happens when you put the `geom_smooth()` function before `geom_point()` instead of after it?

- What does this tell you about how the plot is drawn? Think about how this might be useful when drawing plots.


<br><br>

## Q3b.
- Change the mappings in the `aes()` function so that you plot Life Expectancy against population (`pop`) rather than per capita GDP.
  - What does that look like?
  - What does it tell you about the unit of observation in the dataset?


<br><br>

## Q3c.
- What happens if you map `color` to `year` instead of `continent`?
  - Is the result what you expected?
  - Think about what class of object `year` is.
  - Remember you can get a quick look at the top of the data, which includes some shorthand information on the class of each variable, by typing `gapminder`.
  - Instead of mapping `color = year`, what happens if you try `color = factor(year)`?

  

<br><br>



# Discussion

<font size = "5">Welcome to our Classwork 4 Discussion Board! 👋 </font>

This space is designed for you to engage with your classmates about the material covered in Classwork 4.

Whether you are looking to delve deeper into the content, share insights, or have questions about the content, this is the perfect place for you.

If you have any specific questions for Byeong-Hak (**@bcdanl**) regarding the Classwork 4 materials or need clarification on any points, don't hesitate to ask here. 

All comments will be stored [here](https://github.com/bcdanl/310/discussions/).

Let's collaborate and learn from each other!