---
title: Classwork 5
subtitle: Graph Tables; Add Labels; Make Notes 
date: 2025-02-10
from: markdown+emoji

fig-width: 9
fig-height: 6
---

```{r}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)
library(DT)
library(socviz)

theme_set(theme_fivethirtyeight()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 90,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



<br>

```{r}
library(tidyverse)
library(ggthemes)
library(socviz)
library(ggrepel)

# Setting a default ggplot theme 
theme_set(theme_fivethirtyeight() +
          theme(strip.background = element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 90,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )

```

Recreate the R code necessary to generate the following graphs.

# Question 1

```{r}
gss_sm <- socviz::gss_sm

DT::datatable(gss_sm) # displaying an interactive data.frame
```

<br>

```{r}
#| echo: false

rel_by_region <- gss_sm |>
    group_by( bigregion, religion ) |>
    summarize( N = n() ) |>
    mutate( freq = N / sum(N),
            pct = round( (freq*100), 0) )

p <- ggplot(rel_by_region, 
            aes(x = pct, 
                y = religion, 
                fill = religion))
p + geom_col(position = "dodge2") +
    labs(x = NULL, 
         y = "Percent", 
         fill = "Religion") +
    guides(fill = FALSE) + 
    facet_grid(~ bigregion)
```

<br><br><br>

# Question 2

```{r}
organdata <- socviz::organdata

DT::datatable(organdata)
```

<br>


<br><br>

## Q2a

```{r}
#| echo: false

by_country <- organdata |> group_by(consent_law, country) |>
  summarize_if(is.numeric, lst(mean, sd), na.rm = TRUE) |>
  ungroup()

p <- ggplot(data = by_country,
            mapping = aes(x = donors_mean, y = reorder(country, donors_mean),
                          color = consent_law))
p + geom_point(size=3) +
    labs(x = "Donor Procurement Rate",
         y = "", color = "Consent Law") +
    theme(legend.position="top")
```

<br><br>

## Q2b

```{r}
#| echo: false

by_country <- organdata |> group_by(consent_law, country) |>
  summarize_if(is.numeric, lst(mean, sd), na.rm = TRUE) |>
  ungroup()

p <- ggplot(data = by_country,
            mapping = aes(x = donors_mean,
                          y = reorder(country, donors_mean)))

p + geom_point(size=3) +
    facet_wrap(~ consent_law, scales = "free_y", ncol = 1) +
    labs(x= "Donor Procurement Rate",
         y= "") 
```



## Q2c
```{r}
#| echo: false
p <- ggplot(data = by_country, mapping = aes(x = reorder(country,
              donors_mean), y = donors_mean))

p + geom_pointrange(mapping = aes(ymin = donors_mean - donors_sd,
       ymax = donors_mean + donors_sd)) +
     labs(x= "", y= "Donor Procurement Rate") + coord_flip()
```

<br><br>

## Q2d
```{r}
#| echo: false

p <- ggplot(data = organdata,
            mapping = aes(x = roads,
                          y = donors,
                          color = world))
p + geom_point() +
    scale_y_continuous(breaks = c(5, 15, 25),
                       labels = c("Five", "Fifteen", "Twenty Five"))
```

<br><br>

## Q2e

```{r}
#| echo: false

p <- ggplot(data = organdata,
            mapping = aes(x = roads,
                          y = donors,
                          color = world))
p + geom_point() +
    scale_color_discrete(labels =
                             c("Corporatist", "Liberal",
                               "Social Democratic", "Unclassified")) +
    labs(x = "Road Deaths",
         y = "Donor Procurement",
        color = "Welfare State")
```

<br><br>

## Q2f

```{r}
#| echo: false

organdata |> 
  ggplot(mapping = aes(x = roads,
                       y = donors,
                       color = consent_law)) + 
  geom_point() +
  facet_wrap(~ consent_law, ncol = 1) +
  guides(color = "none") + 
  labs(x = "Road Deaths",
       y = "Donor Procurement")
```

<br><br>


## Q2g

```{r}
#| echo: false

organdata |> 
  ggplot(mapping = aes(x = roads,
                       y = donors,
                       color = consent_law)) + 
  geom_point() +
  labs(title = "By Consent Law",
    x = "Road Deaths",
    y = "Donor Procurement", 
    color = "Legal Regime:") + 
  theme(legend.position = "bottom", 
        plot.title = element_text(color = "darkred",
                                  face = "bold"))
```


<br><br><br>


# Question 3

```{r}
mtcars <- datasets::mtcars
mtcars <- mtcars %>%   # A native pipe (|>) does not work here.
  mutate(car = rownames(.))
rownames(mtcars) <- 1:nrow(mtcars)

DT::datatable(mtcars)
```

<br>

```{r}
#| echo: false

dat <- filter(mtcars, 
              wt > 5 & mpg < 15)

p <- ggplot() + 
  geom_point(data = mtcars, 
             aes(wt, mpg), 
             color = 'red')
p1 <- p + geom_text_repel(data = dat, 
                          aes(wt, mpg, 
                              label = car))
p1
```

<br><br><br>


# Discussion

<font size = "5">Welcome to our Classwork 5 Discussion Board! 👋 </font>

This space is designed for you to engage with your classmates about the material covered in Classwork 5.

Whether you are looking to delve deeper into the content, share insights, or have questions about the content, this is the perfect place for you.

If you have any specific questions for Byeong-Hak (**@bcdanl**) regarding the Classwork 5 materials or need clarification on any points, don't hesitate to ask here. 

All comments will be stored [here](https://github.com/bcdanl/310/discussions/).

Let's collaborate and learn from each other!